% Chapter Template

\chapter{Introduction} % Main chapter title

\label{Chapter1} % Change X to a consecutive number; for referencing this chapter elsewhere, use \ref{ChapterX}

\lhead{Chapter 1. \emph{Introduction}} % Change X to a consecutive number; this is for the header on each page - perhaps a shortened title

%------------------------------------------------------------------------------
%	SECTION 1
%------------------------------------------------------------------------------

\section{Motivation}

Because blind people unable to see the way clearly. They have to use a cane to check for surrounding objects. They have to swing the cane around their vicinity in order to verify their surroundings before making a move. Sometimes, blind people get themselves injured due to unaware surface level difference on a floor or ceiling. Blind people have to able to use cane effectively. Skillful enough to identify and navigate through the environment.

%------------------------------------------------------------------------------
%	SECTION 2
%------------------------------------------------------------------------------

\section{Objectives} 
To assist visually impaired person navigate their way through the environment. Avoiding obstacle collision as many as possible using a portable device

\section{Problem Statement}
Blind people may not be able to assess far obstacles effectively and have to be constantly aware of surroundings.

\section{Scope of Work}
Monitoring distance of surrounding obstacles on head, hips, and differences in floor level. The system also able to detect presence of one person not a group of people according to image captured from raspberry pi camera module. The person have to be looking at the camera and not too far away from the user. To narrow down scopes further, the system should perform indoors with no varying light condition.

\section{Technical Background}
LINUX SHELL SCRIPTING
Linux batch script is a shell script containing series of commands. Shell script allows programmer to program commands in chains and have the system execute them as script events. Similar to batch scripts, the difference is that shell script allows to use programming functions such as conditional statements, loop, and so forth. Shell script can interface directly with operating system where system’s commands are accessible.

HAAR-LIKE FEATURE CASCADE – A FACIAL LEARNING ALGORITHM
Haar-feature-based cascade classifier is an image learning algorithm. The algorithm is looking for common features called Haar-like features. Each feature is a single value obtained by subtracting sum of pixels under white rectangle from sum of pixels under black rectangle. White pixels represents bright part of a gray scale image whereas black pixels is the dark part of the image.

ULTRASONIC SENSOR
Ultrasonic sensors work on a principle similar to sonar which evaluate distance of a target by interpreting the echoes from ultrasonic sound waves. The sensor transmits an ultrasonic wave and produces an output pulse that corresponds to the time required for the burst echo to return to the sensor. By measuring the echo pulse width, the distance to target can easily be calculated.


